Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
results

As a comparison measure, we used the performance of the classifiers on predicting the cognitive state that the subject was in. Table~\ref{tab:results} illustrates the overall performance of . Rows indicate various feature selection methods. The letter \emph{M} means Columns depict the used classifiers. For the classifiers depicted with (*), we used different structure for the data that we fit to them (take example from section where the selection is introduced).

explain the symbols on the table, explain what rows (feature selection methods) are and what columns are (different classifiers and some of them with different structure on the data)

first column naive bayes with pca 148 components, others common feature selection methods as described in Section~\ref{sec:featureSelection}

* means different structure of the data

classifiers performance do not differ significantly

because even PCA has accuracy 61.5\% we can be sure that all the classifiers differ significantly from 50\%

mention confidence interval (how much percent sure we are that the actual accuracy of the classifier is between these regions)

>>>>

As a comparison measure, we used the performance of the classifiers on predicting the cognitive state that the subject was in. Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. The letter \emph{M} denotes Columns depict the used classifiers. For the classifiers depicted with (*), we used different structure for the data that we fit to them (take example from section where the selection is introduced).

%explain the symbols on the table, explain what rows (feature selection methods) are and what columns are (different classifiers and some of them with different structure on the data)

%first column naive bayes with pca 148 components, others common feature selection methods as described in Section~\ref{sec:featureSelection}

%* means different structure of the data

%classifiers performance do not differ significantly

%because even PCA has accuracy 61.5\% we can be sure that all the classifiers differ significantly from 50\%

%mention confidence interval (how much percent sure we are that the actual accuracy of the classifier is between these regions)
